Improving reproducibility of scientific software using Nix/NixOS: A case study on the preCICE ecosystem

### 2024-08-20 paper/paper.tex
feat: consistent naming for section

In this paper, we analyze how well Nix and NixOS can improve reproducibility of scientific software.
To this end, we study the preCICE ecosystem~\cite{preCICEv2} as an example.
preCICE is a coupling library for partitioned multiphysics simulations.
The ecosystem includes diverse legacy solvers, adapters, language bindings, and tutorials besides the coupling library itself making it a challenging and representative testcase.
We try to build the complete ecosystem using Nix and run all tutorials.
Section~\ref{sec:background} briefly introduces the background of Nix and preCICE. Section~\ref{sec:results} then presents the case study including challenges, workarounds, and open problems.
Afterwards, we discuss the results in section~\ref{sec:discussion}, followed by the conclusions in section~\ref{sec:conclusion}.
This paper is the result of a student research project and a streamlined version of its report~\cite{studentreport}.
Beyond the content of this paper, the report also includes a detailed comparison of Nix to Spack and EasyBuild, and a discussion on how to use Nix on HPC systems.

@@

This chapter gives a short introduction into Nix and preCICE.

>>>>

In this paper, we analyze how well Nix and NixOS can improve reproducibility of scientific software.
To this end, we study the preCICE ecosystem~\cite{preCICEv2} as an example.
preCICE is a coupling library for partitioned multiphysics simulations.
The ecosystem includes diverse legacy solvers, adapters, language bindings, and tutorials besides the coupling library itself making it a challenging and representative testcase.
We try to build the complete ecosystem using Nix and run all tutorials.
Section~\ref{sec:background} briefly introduces the background of Nix and preCICE. Section~\ref{sec:results} then presents the case study including challenges, workarounds, and open problems.
Afterwards, we discuss the results in Section~\ref{sec:discussion}, followed by the conclusions in Section~\ref{sec:conclusion}.
This paper is the result of a student research project and a streamlined version of its report~\cite{studentreport}.
Beyond the content of this paper, the report also includes a detailed comparison of Nix to Spack and EasyBuild, and a discussion on how to use Nix on HPC systems.

@@

This Section gives a short introduction into Nix and preCICE.
